### 2013-10-18 chi2014/conclusions.tex
so close

\begin{itemize}
\item The rate of idea and category generation decays non-linearly over time. 
\item Common ideas are more likely to be proposed early in a run. 
\item Conversely, ideas beyond the first 20 are rarer and more original, as measured by o-scores. %This relationship also holds for idea categories.
\item Ideas are more likely to be followed by another idea from the same category than would be expected by random chance.
\item The time it takes to generate an idea when changing categories is longer than the time taken when generating ideas within a category.
\item There are repeatedly observable strategies employed by workers brainstorming in microtask marketplaces
\end{itemize}

>>>>

\begin{itemize}
\item The rate of idea and category generation decays non-linearly over time. 
\item Common ideas are more likely to be proposed early in a run. Conversely, ideas beyond the first 20 are rarer and more original, as measured by o-scores. %This relationship also holds for idea categories.
\item Ideas are more likely to be followed by another idea from the same category than would be expected by random chance. The time it takes to generate an idea is longer when changing categories.
\item There are repeatedly observable strategies employed by workers brainstorming in microtask marketplaces
\end{itemize}

### 2013-10-18 chi2014/introduction.tex
so close

A particularly compelling use of microtask marketplaces is to tap into the collective creativity of crowds. This enables one to quickly sample a wide range of ideas from a diverse population for tasks such as brainstorming or design. Aaron Koblin's art piece ``The Sheep Market'' \cite{koblin_2009} was an early demonstration of this application. In this project, he asked 10,000 individuals to draw a ``sheep facing left,'' yielding a wide range of unique results.

In this paper, we focus on crowd-based brainstorming. While brainstorming has been an implicit component of many creative endeavors in microtask marketplaces, we are unaware of any research that describes and models the brainstorming process in this environment. Furthermore, while there is a rich literature describing brainstorming processes of individuals and groups (e.g., \cite{osborn_applied_1957, pinsonneault_electronic_1999, nijstad_how_2006,brown1998modeling}), there are important qualitative differences in microtask marketplaces. For example, crowd workers exhibit high variance of effort in completing a task \cite{soylent}. Brainstorming participants in a microtask marketplace are paid for their participation, and some might be more eager than others to complete a task as fast as possible to maximize earnings \cite{kittur2008crowdsourcing}. Furthermore, participants in microtask marketplaces cannot be expected to be spatially or temporally co-located. Collectively, these differences make it unclear how brainstorming unfolds in this context.

@@

This paper presents the results of a series of experiments intended to model brainstorming in microtask marketplaces (specifically, Amazon's Mechanical Turk). In our experiments, we asked individuals to brainstorm ways to use an MP3 player whose batteries were dead. We varied the number of ideas requested (5, 10, 20, 50, 75, 100, or unlimited), paying a fixed amount per idea (3.5 cents). Across all conditions, 154 workers submitted responses to 170 HITs (Human Intelligence Tasks), yielding 3292 ideas. From these ideas, we present a series of models characterizing features of crowd brainstorming: the rate of novel idea production, the rate at which novel {\em categories\/} of ideas are produced, qualities of the ideas (for example, whether they are common or not), and characteristics of the brainstorming process itself.

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model, decreasing exponentially over time.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Given our results, we find there is little value in requesting fewer than 20 ideas from workers, since these early ideas are among the most common.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item we identify and describe a set of strategies employed by crowd workers that result in distinct kinds of produced ideas
\end{itemize}

@@

Our results provide baseline models useful for two audiences: 1) those who wish to leverage crowds for brainstorming, and 2) researchers interested in developing techniques to optimize the crowd brainstorming processes. For the former, our models provide recommendations for parameters of brainstorming in this environment (such as the number of questions to request from workers). For the latter group, our models provide a baseline for comparing novel techniques intended to increase the quality of brainstorming output by crowds.

>>>>

A particularly compelling use of microtask marketplaces is to tap into the collective creativity of crowds. Aaron Koblin's art piece ``The Sheep Market'' \cite{koblin_2009} was an early demonstration of this application. %In this project, he asked 10,000 individuals to draw a ``sheep facing left,'' yielding a wide range of unique results.

In this paper, we model brainstorming in microtask marketplaces (specifically, Amazon's Mechanical Turk). 
While brainstorming has been an implicit component of many creative endeavors in microtask marketplaces, we are unaware of any research that describes and models the brainstorming process in this environment. Furthermore, while there is a rich literature describing brainstorming processes of individuals and groups (e.g., \cite{osborn_applied_1957, pinsonneault_electronic_1999, nijstad_how_2006,brown1998modeling}), there are important qualitative differences in microtask marketplaces. For example, crowd workers exhibit high variance of effort in completing a task \cite{soylent}. Brainstorming participants in a microtask marketplace are paid for their participation, and some might be more eager than others to complete a task as fast as possible to maximize earnings \cite{kittur2008crowdsourcing}. Furthermore, participants in microtask marketplaces cannot be expected to be spatially or temporally co-located. Collectively, these differences make it unclear how brainstorming unfolds in this context.

@@

We asked individuals to brainstorm ways to use an MP3 player whose batteries were dead. We varied the number of ideas requested (5, 10, 20, 50, 75, 100, or unlimited), paying a fixed amount per idea (3.5 cents). Across all conditions, 154 workers submitted responses to 170 HITs (Human Intelligence Tasks), yielding 3292 ideas. From these ideas, we present a series of models characterizing features of crowd brainstorming: the rate of novel idea production, the rate at which novel {\em categories\/} of ideas are produced, qualities of the ideas (for example, whether they are common or not), and characteristics of the brainstorming process itself.

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model, decreasing exponentially over time.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Given our results, we find there is little value in requesting fewer than 20 ideas from workers, since these early ideas are among the most common.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. %We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item we identify and describe a set of strategies employed by crowd workers that result in distinct kinds of produced ideas
\end{itemize}

@@

Our results provide baseline models useful for two audiences: 1) those who wish to leverage crowds for brainstorming, and 2) researchers interested in developing techniques to optimize the crowd brainstorming processes. For the former, our models provide recommendations for number of questions to request from workers. For the latter group, our models provide a baseline for comparing novel techniques intended to increase the quality of brainstorming output.

### 2013-10-18 chi2014/qualitative.tex
so close

We selected 30 brainstorming runs (5 randomly from each condition). The primary author applied an open coding strategy, identifying \emph{strategies}: plans or rules that aid in generating ideas. We describe the observed strategies in detail below.
We describe the distribution of these strategies across runs and comment on variability between participants.

@@

Under the problem scoping strategy, the original problem is transformed to a new problem of reduced scope.
Many transformations of the MP3 problem are possible, for example: brainstorm uses for \emph{an audio output device}; brainstorm uses for \emph{a hard drive}; and so on. The participant chooses a problem transformation and generates solutions, each of which is also a solution to the original problem. For example (PXXX):

@@

The participant's responses satisfy the transformed question "brainstorm uses for an audio output device". Resulting ideas no not rely on other aspects of the problem.

We distinguish between two types of problem scoping. \emph{Inward scoping} transformations reduce scope by limiting consideration to a single detail of the problem. The previous responses, which focus on audio output, are an example of inward scoping.

@@

These solutions could be applied to a wide body of problems unrelated to the original, such as "brainstorm uses for a broom".
In contrast, inward scoping solutions are applicable to the transformed problem and the original problem, but not many others. Thus, a useful rule for distinguishing the types of scoping is to consider whether the \emph{set of problems solved by the solutions} is small, or large.

@@

%The strategies above describe techniques for taking one idea and transforming it into another.
In this section, we describe patterns of \emph{where} participants implemented strategies.

@@

\subsection{Variability of Worker Input}
While we observed that individuals are likely to draw from a common pool of ideas early on in the brainstorming process, there were outliers in the data. For example, one individual in the 75 ideas condition consistently produced some of most original ideas for old MP3 players:

\begin{itemize}
\item With displays - could be attached to a small solar panel (like the USB chargers w/multi attachments, including solar and car, etc.) and all the power could be sent to the screen as a small, portable light, then sent to countries lacking power in rural areas.
\item They could be loaded with coordinates or other info and sealed in containers, then used in ocean current studies - once the container was collected they could be plugged in and read, and the data could be sent to whomever.
%\item They could be plugged in at a base camp at the bottom of Everest, and then potential climbers could record their name, loved ones' address, and any last words before attempting the climb. 
\end{itemize}

This individual's responses raised the observed uniqueness of ideas in the 75 condition. 
In contrast, other individuals filled their quotas with excessive repeat riffing chains.

This variability in worker responses prevented us from modeling any potential effects that the number of questions requested might have on individuals' responses. Thus, while it is clear that there is little advantage to requesting 5 or 10 ideas from workers, it is not clear whether it is preferable to request 20, 50, 75, or 100 ideas. We suspect that requesting 50 or 75 is the ``sweet'' spot, but are not able to empirically support that recommendation at this time.

>>>>

We selected 30 brainstorming runs (5 randomly from each condition). The primary author applied an open coding strategy, identifying \emph{strategies}: plans or rules that aid in generating ideas. We describe the observed strategies in detail below.

@@

Under the problem scoping strategy, the original problem is transformed to a new problem of reduced scope.
Many transformations of the MP3 problem are possible, for example: brainstorm uses for \emph{an audio output device}; brainstorm uses for \emph{a hard drive}; and so on. For example (PXXX):

@@

The participant's responses satisfy the transformed question "brainstorm uses for an audio output device", and satisfy the original problem.

We distinguish between two types of problem scoping. \emph{Inward scoping} transformations reduce scope by limiting consideration to a single detail of the problem. The previous responses, which focus on audio output, are an example of inward scoping. Response generated by inward scoping are applicabable to the transformed problem and the original problem, but few others.

@@

These solutions could be applied to a wide body of problems unrelated to the original, such as "brainstorm uses for a broom".
Thus, a useful rule for distinguishing the types of scoping is to consider whether the \emph{set of problems solved by the solutions} is small, or large.

@@

%The strategies above describe techniques for taking one idea and transforming it into another.
%In this section, we describe patterns of \emph{where} participants implemented strategies.

@@

%\subsection{Variability of Worker Input}
%While we observed that individuals are likely to draw from a common pool of ideas early on in the brainstorming process, there were outliers in the data. For example, one individual in the 75 ideas condition consistently produced some of most original ideas for old MP3 players:

%\begin{itemize}
%\item With displays - could be attached to a small solar panel (like the USB chargers w/multi attachments, including solar and car, etc.) and all the power could be sent to the screen as a small, portable light, then sent to countries lacking power in rural areas.
%\item They could be loaded with coordinates or other info and sealed in containers, then used in ocean current studies - once the container was collected they could be plugged in and read, and the data could be sent to whomever.
%%\item They could be plugged in at a base camp at the bottom of Everest, and then potential climbers could record their name, loved ones' address, and any last words before attempting the climb. 
%\end{itemize}
%
%This individual's responses raised the observed uniqueness of ideas in the 75 condition. 
%In contrast, other individuals filled their quotas with excessive repeat riffing chains. 
%
%This variability in worker responses prevented us from modeling any potential effects that the number of questions requested might have on individuals' responses. Thus, while it is clear that there is little advantage to requesting 5 or 10 ideas from workers, it is not clear whether it is preferable to request 20, 50, 75, or 100 ideas. We suspect that requesting 50 or 75 is the ``sweet'' spot, but are not able to empirically support that recommendation at this time.
